---
title: Codemeta Terms

---

```{r echo=FALSE, include = FALSE, message = FALSE}
knitr::opts_chunk$set(echo=FALSE, message = FALSE, warning = FALSE)
library("readr")
library("dplyr")
```

* Permalink: <https://w3id.org/codemeta/3.0>
* CodeMeta version: 3.0

## Terms from Schema.org

Recognized properties for CodeMeta `SoftwareSourceCode` and `SoftwareApplication` includes the following terms from <https://schema.org>.  These terms are part of the CodeMeta specification and can be used without any prefix.

```{r}
crosswalk <- "https://github.com/codemeta/codemeta/raw/master/crosswalk.csv"
cw <- read_csv(crosswalk)
cw %>%
  filter(grepl("schema:(SoftwareSourceCode|SoftwareApplication|CreativeWork|Thing)", `Parent Type`)) %>%
  select(Property, Type, Description)  %>%
knitr::kable("html", table.attr="class=\"table table-striped\"")
```

These terms are all recognized properties of <https://schema.org/SoftwareSourceCode> or <https://schema.org/SoftwareApplication> Types. Note that while most properties take basic data types as values (`Text`, `URL`), several take other node types, such as `Person` or `Organization`.  Recommended fields for these node types in CodeMeta documents are given below.

```{r}
cw %>%
  filter(grepl("schema:(Person|Thing)", `Parent Type`)) %>%
  select(Property, Type, Description)  %>%
knitr::kable("html", table.attr="class=\"table table-striped\"")
```

## Codemeta terms

The CodeMeta project also introduces the following additional properties, which lack clear equivalents in <https://schema.org> but can play an important role in software metadata records covered by the CodeMeta crosswalk.

* Namespace: <https://codemeta.github.io/terms/>
  - **Warning**: This namespace will change to be w3id-based for CodeMeta 4.0

```{r}
cw %>%
  filter(grepl("codemeta:", `Parent Type`)) %>%
  select(Property, Type, Description)  %>%
knitr::kable("html", table.attr="class=\"table table-striped\"")

```


Please suggest additional terms or adjustments to this representation in the [codemeta issues](https://github.com/codemeta/codemeta/issues)
